Synthesizing Quotient Lenses

### 2018-05-07 papers/QuotientLenses/main.tex
Commented out some suggestions

This paper applies this idea to the problem of
synthesizing {\em quotient lenses}~\cite{quotientlenses}.
Quotient lenses are lenses in which the lens laws are
loosened so that they hold modulo an equivalence relation on the source and
target data respectively; in this paper we are concerned with {\em bijective
quotient lenses} which are lenses for which Equation \ref{bijectivelenslaws}
holds modulo equivalence relations $\equiv_S$ and $\equiv_T$ defined on the source
and target data respectively:\bcp{Not too convinced about the colors.  The
  fact that lens expressions mix black and red is distracting -- my eyes
  can't easily tell which bits of a larger expression are lenses.  I would
  suggest either:
  \begin{itemize}
  \item get and put italicized, plus
  \item either and lens expressions (completely) in some subtle color (maybe
  brown), or simply black.
  \end{itemize}
}\saz{I agree that the coloring can be a bit distracting, but I do think that
  highlighting the keywords in the code helps for parsing--maybe using dark blue
  is better? Why do ``get'' and ``put'' deserve special treatment as keywords,
  compared to, say, ``synth'' or ``del''?}
%
\bcp{This gets at the basic difficulty with code coloring: we are dealing,
  in different parts of the paper, with (1) Boomerang code and (2)
  mathematical expressions involving lenses. We might want to make different
  highlighting choices in the two cases (e.g., we might want to highlight
  just individual keywords in large pieces of code, rather than the whole
  thing, while lens expressions within larger math formulas should perhaps
  be colored all the same, to better distinguish them from their context.
  My suggestion for get and put was based on the fact that they are not
  really part of boomerang programs: they are only mathematical entities (I
  think you {\em can} extract them as separate functions in boomerang, but
  usually there is no reason to, and we don't do it here).  However, I think
  it doesn't matter that much and we should use our remaining time now for
  polishing the text.  I propose we try dark blue for today and, if it's not
  distracting, just leave it alone.}
%
\begin{equation}\label{quotientlenslaws}
\ell.\get \; (\ell.\lput \; t) \equiv_T t \text{, and } \ell.\lput \; (\ell.\get
\; s) \equiv_S s
\end{equation}
Quotient lenses are useful in situations where a programmer wishes for the
transformation defined by a lens to have the same behavior on data that differ
only in inessential details. For instance, a programmer may wish to ``quotient
away'' the number of white space characters between data items, the
capitalization of various strings, the sequence of fields in a record, or the
order of items in a list.

>>>>

This paper applies this idea to the problem of
synthesizing {\em quotient lenses}~\cite{quotientlenses}.
Quotient lenses are lenses in which the lens laws are
loosened so that they hold modulo an equivalence relation on the source and
target data respectively; in this paper we are concerned with {\em bijective
quotient lenses} which are lenses for which Equation \ref{bijectivelenslaws}
holds modulo equivalence relations $\equiv_S$ and $\equiv_T$ defined on the source
and target data respectively:
\iflater
\bcp{Not too convinced about the colors.  The
  fact that lens expressions mix black and red is distracting -- my eyes
  can't easily tell which bits of a larger expression are lenses.  I would
  suggest either:
  \begin{itemize}
  \item get and put italicized, plus
  \item either and lens expressions (completely) in some subtle color (maybe
  brown), or simply black.
  \end{itemize}
}\saz{I agree that the coloring can be a bit distracting, but I do think that
  highlighting the keywords in the code helps for parsing--maybe using dark blue
  is better? Why do ``get'' and ``put'' deserve special treatment as keywords,
  compared to, say, ``synth'' or ``del''?}
%
\bcp{This gets at the basic difficulty with code coloring: we are dealing,
  in different parts of the paper, with (1) Boomerang code and (2)
  mathematical expressions involving lenses. We might want to make different
  highlighting choices in the two cases (e.g., we might want to highlight
  just individual keywords in large pieces of code, rather than the whole
  thing, while lens expressions within larger math formulas should perhaps
  be colored all the same, to better distinguish them from their context.
  My suggestion for get and put was based on the fact that they are not
  really part of boomerang programs: they are only mathematical entities (I
  think you {\em can} extract them as separate functions in boomerang, but
  usually there is no reason to, and we don't do it here).  However, I think
  it doesn't matter that much and we should use our remaining time now for
  polishing the text.  I propose we try dark blue for today and, if it's not
  distracting, just leave it alone.}
%
\fi
\begin{equation}\label{quotientlenslaws}
\ell.\get \; (\ell.\lput \; t) \equiv_T t \text{, and } \ell.\lput \; (\ell.\get
\; s) \equiv_S s
\end{equation}
Quotient lenses are useful in situations where a programmer wishes for the
transformation defined by a lens to have the same behavior on data that differ
only in inessential details. For instance, a programmer may wish to ``quotient
away'' the number of white space characters between data items, the
capitalization of various strings, the sequence of fields in a record, or the
order of items in a list.
